\recipe[It has coffee, so eat it for the energy.]{Browned Butter Brownies}{Gage}
\serves{4}
\preptime{30 minutes}
\cooktime{30 minutes}
\dishtype{}
\begin{ingreds}
    1$\frac{1}{2}$ sticks unsalted butter
    4 oz (113 grams) semisweet chocolate (chopped)
    $\frac{1}{2}$ cup (100 grams) sugar
    $\frac{1}{2}$ cup (100 grams) light brown sugar
    3 large eggs
    1 tsp vanilla extract
    $\frac{1}{2}$ cup (64 grams) all-purpose flour
    $\frac{1}{2}$ cup (43 grams) unsweetened cocoa powder
    $\frac{1}{2}$ teaspoon instant espresso powder
    $\frac{1}{2}$ teaspoon fine salt
    1 cup (170 grams) semisweet chocolate chips
\end{ingreds}
\begin{method}[Preheat the oven to \temp{350}.]
    Grease a glass 8'' square pan.
    In a small saucepan set over medium low heat, melt the butter.\par
    Swirling the pan occasionally, continue to cook the butter, increasing the heat to medium. It should become foamy with audible crackling and popping noises.\par
    Once the crackling stops, continue to swirl the pan until the butter develops a nutty aroma and brown bits start to form at the bottom. Do not allow the bits to burn!\par
    Once the bits are amber in color, ($\sim$2--3 minutes after the popping stops) remove from heat and pour into a mixing bowl, scraping the brown bits into the bowl.\par
    Quickly add in the chopped chocolate and stir until melted.\par
    In the bowl of an electric mixer fitted with the whisk attachment, combine the sugar, brown sugar, eggs, and vanilla.\par
    Beat on high speed until completely thickened and fluffy in texture and lightened in color, $\sim$8 minutes.\par
    On low speed, gradually pour in the butter/chocolate mixture.\par
    Using a rubber spatula, fold in the flour, cocoa, espresso, and salt until just combined.\par
    Fold in the chocolate chips.\par
    Pour into the prepared pan and smooth out with a spatula.\par
    Bake for 22--25 minutes, or until set but not overbaked.\par
    Let cool completely before slicing and serving.       
\end{method}