\recipe[Delicious and savory.]{Browned Butter Cornbread}{Gage}
\serves{4}
\preptime{1 hour}
\cooktime[Cook time]{25 minutes}
\dishtype{\bread}
\dishother{\vegetarian}
\begin{ingreds}
    $\frac{1}{2}$ cup (112 g) unsalted butter
    $\frac{1}{2}$ bunch of sage
    $\frac{1}{2}$ bunch of thyme
    1$\frac{1}{4}$ cups (188 g) all-purpose flour
    $\frac{1}{3}$ cup (67 g) sugar
    3$\frac{1}{2}$ tbsp (47 g) brown sugar
    1$\frac{1}{4}$ tsp (8 g) kosher salt
    1 tbsp (13 g) baking powder
    1$\frac{1}{4}$ cups (175g) finely ground yellow cornmeal
    2 large eggs
    1$\frac{1}{2}$ cups buttermilk
\end{ingreds}
\begin{method}[Preheat an 8” cast-iron skillet in the oven at \temp{400}]
    In a small pot, melt the butter over medium heat. Once melted, continue cooking to brown the butter until it turns dark brown. Then turn off the heat.\par
    Add the sage and thyme, stir to combine, transfer the butter-herb mixture to a separate container, and set aside to cool.\par
    In a bowl, whisk together the flour, sugar, brown sugar, salt, baking powder, and cornmeal.\par
    In a separate bowl, whisk the eggs, then whisk in the buttermilk.
    Discard the herbs from the slightly cooled butter. In a slow stream, whisk the butter into the buttermilk mixture. Then whisk the wet mixture into the dry mixture until completely smooth and combined.\par
    Remove the hot pan from the oven, and lightly grease it with cooking spray. Add the batter to the pan, and spread it evenly.\par
    Bake for 20--25 min, or until a toothpick inserted into the center comes out clean. 
    Cool for a few minutes in the pan and then remove to a cooling rack to cool completely.\par
\end{method}