\recipe[Raleigh's favorite meal of all time.]{Butter Chicken}{Gage}
\serves{4}
\preptime{30 minutes}
\cooktime{30 minutes}
\dishtype{}
\begin{ingreds}
    \ingredients[Marinade]
        1$\frac{1}{2}$ lbs chicken thighs (1'' pieces)
        $\frac{3}{4}$ cup (145g) yogurt
        2$\frac{1}{2}$ tsp (6g) chili powder
        1 tsp (2g) turmeric
        2 tsp lemon juice
        1 tsp (2g) cumin
        1 tbsp (7g) Garam masala
        2 teaspoons (10g) fine sea salt
        2-inch knob ginger
    \columnbreak{}
    \ingredients[Curry Sauce]
        1 onion, thinly sliced
        5 garlic cloves, chopped
        1 tsp (2g) garam masala
        1 tsp (2g) chili powder
        $\frac{1}{2}$ tsp (1g) turmeric
        $\frac{1}{2}$ tsp (1g) fenugreek
        1 tbsp (13g) sugar
        2 tbsp (28g) ghee
        1 tbsp (15g) grated ginger
        1 large can crushed tomatoes
        $\frac{3}{4}$ cup (177ml) heavy cream
        2 tbsp (28g) unsalted butter
        fresh cilantro for garnish
        salt to taste
\end{ingreds}
\begin{method}[Requires $>$30 minutes of marination.]
    Place your chicken thighs in a bowl along with the rest of the marinade ingredients and mix thoroughly, ensuring the chicken gets completely coated with the marinade.\par
    Cover with plastic wrap and reserve in the refrigerator.\par
    Heat a 12'' nonstick skillet over medium-high heat and add the ghee.\par
    Once melted, add your marinated chicken pieces and sear them on all sides until golden brown. It is okay if it does not get cooked all the way through.\par
    Remove your chicken, place it in a large bowl, and reserve.\par
    Add the onions, season with salt, and cook until just translucent.\par
    Add the garlic and ginger and cook for another 30 seconds.\par
    Stirring often, add the garam masala, chili powder, turmeric, fenugreek, and sugar.\par
    Add in your crushed tomatoes and reduce for 2 minutes.\par
    Place the onion mix in the blender and blend on high until smooth.\par
    Place the sauce back in the pan, add your chicken, cover with a lid and simmer for seven minutes.\par
    Add the heavy cream and simmer until thickened.\par
    Cut the heat, stir in butter, and season with salt to taste.\par
    Serve your chicken over rice, and garnished with cilantro.    
\end{method}