\recipe[Why fuss with rice, if you can just use orzo?]{Chicken Orzo Soup}{Gage}
\serves{4}
\preptime{20 minutes}
\cooktime{45 minutes}
\dishtype{\soup}
\begin{ingreds}
    1 tbsp olive oil
    6 garlic cloves (minced)
    1 yellow onion (diced)
    2 carrots (thinly sliced)
    2 celery stalks (chopped)
    1 tbsp fresh ginger
    1 tsp cayenne
    1 tsp ground turmeric
    6 cups chicken broth
    1 lb chicken breast/thighs
    1 tsp chopped rosemary
    1 tsp chopped thyme
    $\frac{1}{2}$ tsp salt
    black pepper (to taste)
    1 cup orzo pasta
    $\frac{2}{3}$ cup frozen peas
\end{ingreds}
\begin{method}[Feel free to substitute with pre-cooked chicken.]
    Place a large dutch oven over medium high heat.\par
    Add the olive oil once the pot is ripping hot and add in the chicken making sure not to crowd the pot.\par
    Get a good sear on all sides of the chicken and save for later. There should be a nice fond in the pan at this point.\par
    Add in the onion, carrots and celery.\par
    Cook for a few minutes until the onion becomes translucent.\par
    Add in the ginger, garlic, and turmeric and saut\'e for 30 seconds.\par
    Add in chicken broth, chicken breast from earlier, and seasonings.\par
    Bring soup to a boil then reduce heat to low and simmer until chicken is fully cooked.\par
    Once chicken is cooked, remove and transfer to a cutting board to shred.\par
    Add chicken back to the pot and stir in frozen peas and orzo.\par
    Cook for another 7--8 minutes until orzo is just barely tender.
\end{method}