\recipe[It's fried chicken my boy.]{Chicken Katsu}{Gage}
\serves{4}
\preptime{20 minutes}
\cooktime{15 minutes}
\dishtype{\main}
\begin{ingreds}
    1$\frac{1}{2}$ cups all-purpose flour
    3 large eggs
    2 tbsp water
    2 cups panko
    4 boneless, skinless chicken breasts/thighs
    2 cups high-heat oil
    kosher salt
\end{ingreds}
\begin{method}
    Place the chicken breasts between two pieces of plastic wrap and pound to an even thickness of $~\frac{1}{2}$''. Season with salt.\par
    Prepare 3 separate shallow bowls for the breading station. In the first, place the flour. In the second, whisk together the eggs and water. In the last, place the panko.\par
    Thoroughly coat each piece of chicken in the flour, shaking off any excess.\par
    Coat evenly in the egg, making sure no dry spots remain.\par
    Finally, coat the chicken on all sides in the panko, pressing to make sure it's thoroughly coated.\par
    Set aside on a piece of parchment paper, and separate each breast with a new layer of parchment.\par
    Fill a large deep cast-iron skillet or heavy-bottomed pot with the oil, and heat over high heat until just shimmering, or about \temp{325--350}.\par
    Carefully place the chicken breast in the oil one at a time.\par
    Fry for 3--5 minutes, or until crispy golden brown.\par
    Flip and fry for an additional 3--5 minutes, or until it reaches an internal temp of 165°F.\par
    Place on a wire rack in a rimmed baking sheet, season again with salt and let drain and cool.\par Repeat with the remaining chicken breasts.\par
    Serve sliced, with a side of spicy cabbage slaw, and drizzled with katsu sauce and Sriracha.
\end{method}