\recipe[This one is worth the effort. I promise!]{Chorizo Tacos with Plantains}{Gage}
\serves{4}
\preptime{15 minutes}
\cooktime{30 minutes}
\dishtype{\main}
\begin{ingreds}
    1 link of chorizo
    1 plantain
    1 lime (juice)
    $\frac{1}{2}$ onion (diced)
    $\frac{1}{2}$ onion (Julienned)
    1 bunch cilantro (chopped)
    queso Oaxaca (or mozzarella)
    6--8 corn tortillas
    vegetable oil
    $\frac{1}{4}$ cup apple cider vinegar
    hot sauce (like Cholula\textsuperscript{\textregistered})
    Mexican lager (like Corona\textsuperscript{\textregistered}) (or water)  
\end{ingreds}
\begin{method}
    In a small container, add the apple cider vinegar, juice of half a lime, and the Julienned onions. Seal and shake briefly and set aside to pickle.\par
    Shred the queso Oaxaca or mozzarella. You won't need much.\par
    Slice the plantain at a bias into $\frac{1}{4}$'' slices.\par
    Heat a non-stick skillet over medium-high heat and add the chorizo. Cook until browned.\par
    Remove the chorizo, and add the onions until translucent.\par
    Deglaze with a $\frac{1}{4}$ cup of the lager (or water) until it boils off, then add back the chorizo.\par
    Mix briefly, then set on the back burner.\par
    In a large deep skillet add the oil so that it just covers the bottom and then some.\par
    Once the oil is shimmering, add the plantain slices in batches, making sure not to overcrowd the pan.\par
    Cook until one side is browned then flip. Once done, set aside.\par
    Heat a non-stick skillet over medium heat until just smoking.\par
    Add the tortillas, and cook both sides so that they are just slightly burned in a few spots.\par
    Store in a bowl covered with a rag, or they will get stale.\par
    Now plate. Add the tortillas, then the cheese. You can melt with a blowtorch or in the microwave. Add the chorizo, then 2--3 slices of plantains, then the pickled onions. Cut a few leaves of cilantro on top with scissors, and spritz with a quarter of lime. Optionally, top with a few dabs of hot sauce.
\end{method}