\recipe[Perfect for making Cubano sandwiches.]{Cubano Bread}{Gage}
\serves{4}
\preptime{2 hours}
\cooktime[Cook time]{35 minutes}
\dishtype{\vegetarian, \bread}
\dishother{\makeahead}
\begin{ingreds}
    1$\frac{1}{4}$ cups water (\temp{100})
    1 tbsp instant dry yeast
    3$\frac{1}{2}$ cups (500g) unbleached bread flour
    1 tbsp (13g) granulated sugar
    2 tsp (12g) fine sea salt
    2$\frac{1}{2}$ tbsp lard, solidified
\end{ingreds}
\begin{method}[Preheat the oven to \temp{400}.]
    In a small bowl, stir together the warm water and yeast. Cover with plastic wrap and let sit for 10 min. The mixture should get slightly foamy, and the yeast should dissolve.\par
    In a stand mixer bowl, add the flour, sugar, and salt. Mix together thoroughly. With the dough hook attachment, start mixing on medium-low speed. Slowly add the warm yeast mixture and the lard. Mix until combined. Once a cohesive dough is formed, keep mixing for another 3 to 5 minutes, or until smooth.\par
    Shape the dough into a ball, and place in a greased bowl covered with greased plastic wrap. Let rise at room temp for 45 min to 1 hr, or until doubled in size.\par
    Punch down the dough to release the gas and place on a lightly floured surface. Divide the dough into 2 even pieces. Cover with a damp towel, and let them rest right where they are for 10 minutes.\par
    Flatten out 1 piece of dough into about a $\frac{1}{2}$-inch thick rectangle, with the long edge $\sim$10'' long.\par
    From the long edge, tightly roll the dough and close the seams at the bottom and sides.\par
    Carefully roll the log while applying pressure outward to \linebreak slightly taper the ends. The log should be $\sim$15'' long.\par
    Repeat with the other piece of dough.\par
    Place the loaves onto a parchment-lined baking sheet 4--6'' apart. Cover with another baking sheet.\par
    Let the dough proof for $>$30 minutes at room temperature.\par
    About 10 minutes before the dough is done proofing, bring a 10'' oven-proof skillet of water to a boil.\par
    Using a spray bottle, lightly spray the dough with water.\par
    Using a razor blade or an extremely sharp knife, score a shallow seam along the length of the loaves.\par
    Place the skillet of boiling water on the bottom rack of the oven.\par
    Place the baking sheet with the dough in the middle of the oven on a separate rack above the water.\par
    Spray the inside of the oven with a little water to generate steam.\par
    Let the bread steam for 8--10 minutes. Reduce the heat to \temp{375}, remove the skillet of water, and let the bread bake for another 20--22 minutes, or until lightly browned.\par
    Let cool completely on a wire rack. Slice and serve. Store on the counter loosely wrapped in a kitchen towel for up to 2 days and then in a resealable bag for 1 more day. Freeze in an airtight container for up to 2 months.\par
\end{method}
% \showit[1.25in]{example-image-b}{This is a picture}