\recipe[Don't think about the carbs. Think about your taste buds.]{Dinner Rolls}{Gage}
\serves{9}
\preptime{2$\frac{1}{2}$ hours}
\cooktime[Cook time]{20--30 minutes}
\dishtype{\bread}
\dishother{\vegetarian}
\begin{ingreds}
    \ingredients[Dough]
        $\frac{1}{2}$ cup whole milk (\temp{100})
        $\frac{1}{2}$ cup water (\temp{100})
        2$\frac{1}{2}$ tsp instant dry yeast
        3$\frac{1}{2}$ cups bread flour
        1 tbsp granulated sugar
        1$\frac{1}{2}$ tsp fine salt
        1 large egg
        1 large egg yolk
        2$\frac{1}{2}$ tbsp unsalted butter (softened)
    \columnbreak{}
    \ingredients[Milk Roux]
        2 tbsp all-purpose flour
        2 tbsp filtered water
        $\frac{1}{4}$ cup whole milk
    \ingredients[For Baking]
        1 egg (beaten)
        $\frac{1}{3}$ cup salted butter
        2 cloves garlic (minced)
        flaky salt
\end{ingreds}
\begin{method}[Preheat the oven to \temp{375}.]
    \submethod{Milk Roux}
        In a small saucepan, whisk together the flour, water, and milk until completely dissolved.\par
        Heat over medium heat, stirring continuously, until the mixture thickens into a thick paste.\par
        Transfer to a small bowl and set aside to cool.
    \submethod{Dough}
        In a bowl, add the warmed milk and water. Stir in the yeast, cover with plastic wrap, and set aside for 10 minutes.\par
        In the bowl of a stand mixer, whisk together the bread flour, sugar, and salt until thoroughly combined.\par
        Fit the stand mixer with the dough hook and mix on medium-low speed.\par
        One at a time, add the yeast mixture, whole egg, and egg yolk.\par
        Once the mixture starts to come together, add the milk roux.\par
        Mix for 3--4 minutes or until the dough is smooth.\par
        Add the butter and continue mixing on medium-low speed until all the butter is incorporated.\par
        Transfer the dough to a large greased bowl and cover with greased plastic wrap.\par
        Let rise at room temperature for 1$\frac{1}{2}$ hours or until the dough has doubled in size.\par
        Punch down the dough to release the gas and turn onto your working surface.
    \submethod{Baking}
        Lightly grease an 8'' square baking pan. Divide the dough into 9 even pieces. Shape each piece into a tight ball by stretching and folding the sides over into the center of the dough.\par
        Roll the dough ball in circles while maintaining constant contact with the work surface until you've formed a tight ball.\par
        In the baking pan, arrange the dough balls in rows of 3. Cover with a damp towel and let proof at room temperature for 30 minutes or until doubled in size.\par
        Brush the proofed rolls with the egg to lightly coat each top.\par
        Bake for 16--20 minutes or until puffed and golden brown.\par
        When they're almost done baking, in a small pot, gently heat the butter over medium heat until melted.\par
        Add the garlic and gently swirl for 10 seconds.\par
        Remove the rolls from the oven and immediately brush with the garlic butter, sprkinkle with the flaky salt, and serve warm for the best texture and flavor.
\end{method}
% \showit[1.25in]{example-image-b}{This is a picture}